---
title: "The Simpsons dataset"
output: github_document
---

```{r echo = FALSE}
library("thesimpsons")
```

This dataset contains the characters, locations, episode details, and script 
lines for approximately 600 Simpsons episodes, dating back to 1989.
Data got from [Kaggle](https://www.kaggle.com/wcukierski/the-simpsons-by-the-data).

This package contains four datasets:

* `characters`: The Simpsons characters information.

```{r}
head(characters)
```

* `episodes`: metadata related to each The Simpsons episode.

```{r}
head(episodes[, 1:6])
```

* `locations`: The Simpsons world locations.

```{r}
head(locations)
```

* `script_lines`: the text spoken during each The Simpsons episode (including details about which character said it and where).

```{r}
head(script_lines[, 1:4])
```

## Examples

### Race plot: spoken words by character by season

```{r, message = FALSE}
library("thesimpsons")
library("dplyr")
library("ggplot2")
library("gganimate")
library("hrbrthemes")
```

```{r}
# merge script lines with characters and episodes data
script_lines %>%
  filter(!is.na(word_count)) %>%
  left_join(characters, by = c("character_id" = "id")) %>%
  left_join(episodes, by = c("episode_id" = "id")) -> script_lines_full

n_chars <- 10 # include only the 10 most speaking characters
script_lines_full %>%
  select(name, word_count, season) %>% # use just char name, word_count, season
  group_by(name, season) %>% # by name & season
  summarise(wc = sum(word_count)) %>% # get the sum of word counts
  mutate(wc_cs = cumsum(wc)) %>% # generate the cum sum of wc
  group_by(season) %>%
  mutate( # create the ranking (top 10 to plot)
    rank = min_rank(-wc_cs) * 1,
    val_lbl = paste0(" ", wc_cs)
  ) %>%
  filter(rank <= n_chars) -> char_wc_by_season

ggp <- ggplot(char_wc_by_season, aes(rank,
  group = name,
  fill = as.factor(name), color = as.factor(name)
))
ggp <- ggp + geom_tile(
  aes(y = wc_cs / 2, height = wc_cs, width = 0.9),
  alpha = 0.8, color = NA
)
ggp <- ggp + 
  geom_text(aes(y = 0, label = paste(name, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y = wc_cs, label = val_lbl, hjust = 0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  labs(
    subtitle = "Words by seasons",
    title = "Season: {closest_state}",
    x = ""
  ) +
  theme_ipsum_rc() +
  theme(
    plot.title = element_text(hjust = 0, size = 22),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    plot.margin = margin(1, 1, 1, 4, "cm")
  )

ggp <- ggp +
  transition_states(season, transition_length = 4, state_length = 1) +
  ease_aes("cubic-in-out")
animate(ggp, nframes = 100, fps = 30, duration = 18)
```
